---
title: "EDA user"
author: "Xiang XU"
date: "November 23, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
pacman::p_load(knitr,ggplot2, tidyverse, dplyr, ggraph, stringr, wordcloud, tidytext,tidyr,lubridate, widyr,jsonlite,sentimentr, benford.analysis, magrittr,wordcloud2, webshot ,htmlwidgets)
webshot::install_phantomjs()

```

###User_info

```{r}
##load prepared data
rm(list = ls())
user_info <- get(load("./Dataset/user_info.Rdata"));rm("df_user_info")

```

look at users' stars density
```{r}
ggplot(user_info, aes(x= average_stars, y =..density..)) + 
  geom_density(fill = "tomato", color =NA, adjust =2)+
  ggtitle("Density of users' stars")
```


look at users' review count density
```{r}

ggplot(user_info, aes(x= review_count, y =..density..)) + 
  geom_density(fill = "salmon", color =NA, adjust =2)+
  ggtitle("Density of users' review count")
```
 
It seems there are some outliers in the review count
```{r}
ggplot(user_info, aes(y= review_count)) + 
  geom_boxplot()+
  ggtitle("Boxplot of users' review count")

summary(user_info$review_count)
```

##### Outliers?
The max value of a user's review count is 12723, it seems impossible, let's look at these guy who have more than 10000 reviews, just out of curiosity.
```{r}
user_review_outliers <- user_info %>%
  filter(review_count >10000) %>%
  arrange(desc(review_count))
user_review_outliers

```
And look at their reviews
```{r}
#review <- get(load("./dataset/review.Rdata"))
# review_restaurant <- review %>%
#   inner_join(restaurant_info, by ="business_id")
#save(review_restaurant, file = "./data/df_review_restaurant.Rdata")
user_review_outliers %<>% inner_join(review_sentiment_restaurant, by = "user_id") %>% unique()%>%
  select(user_id,name.x,stars.x, review_count.x,date, stars.y, review_sentiment)
user_review_outliers
```
These review and stars seem fair to me.

#####Remove outliers

To detect the outliers I use the command boxplot.stats()$out which use the Tukey’s method to identify and temporarily remove the outliers ranged above and below the 1.5*IQR.

```{r}
View(user_info)

length(boxplot.stats(user_info$review_count)$out)

user_rm_outlier <- user_info
source("http://goo.gl/UUyEzD")
outlier_action <- outlierKD(user_rm_outlier, review_count)

user_rm_outlier %<>% na.omit()

summary(user_rm_outlier$review_count)

ggplot(user_rm_outlier, aes(y= review_count)) + 
  geom_boxplot()#+ geom_violin()
  #ggtitle("Boxplot of users' review count")
ggplot(user_rm_outlier, aes(x= review_count, y =..density..)) + 
  geom_density(fill = "salmon", color =NA, adjust =2)+
  ggtitle("Density of users' review count")

```



####Correlations
Is there realations between review count, yelping-year, gender, n_friends and stars?

#####Yelping year
```{r}
#generatte a variable for how many years ahs a user been "yelping"
user_rm_outlier$yelping_year <- 2018 - year(user_rm_outlier$yelping_since)
unique(user_rm_outlier$yelping_year)


#factorize yelping years into 4 levels
#i <- 1
for(i in 1:nrow(user_rm_outlier)) {
  if(user_rm_outlier$yelping_year_level[i]== "0-2 yrs") {user_rm_outlier$yelping_year_level_factor[i] <- 1}
  else{
    if(user_rm_outlier$yelping_year_level[i]=="3-5 yrs" ) {user_rm_outlier$yelping_year_level_factor[i] <- 2}
    else{
      if(user_rm_outlier$yelping_year_level[i]=="6-9 yrs") {user_rm_outlier$yelping_year_level_factor[i] <- 3}
      else{
        user_rm_outlier$yelping_year_level_factor[i] <- 4
      }
    }
  }
  
  # i <- i+1
  # if(i > nrow(user_rm_outlier)) break
}

user_rm_outlier$yelping_year_level <- as.factor(user_rm_outlier$yelping_year_level)

temp <- user_rm_outlier %>% select(c(user_id,review_count, average_stars,yelping_year_level))
levels(temp$yelping_year_level) <- c("0-2 yrs" , "3-5 yrs" ,"6-9 yrs" , "> 10 yrs")
ggplot(temp, aes(x= review_count, y =..density.. )) + 
  geom_density(fill = "salmon", color =NA, adjust =2)+
  facet_grid(yelping_year_level ~.)+
  ggtitle("Density of users' review count by yelping year")


ggplot(temp, aes(x= average_stars, y =..density.. ,group = yelping_year_level)) + 
  geom_density(fill = "salmon", color =yelping_year_level, adjust =2)+
  #facet_grid(yelping_year~.)+
  ggtitle("Density of users' stars by yelping year")


ggplot(user_rm_outlier, aes(x= factor(yelping_year_level),y= review_count)) + 
  geom_boxplot()+
  #geom_boxplot(aes(group= yelping_year_level))+
  ggtitle("Boxplot of users' review count by yelping year")

  
position=position_jitter(width=.3, height=.08)
```

###WordCloud

```{r}

#star0.review <- df_review_restaurant %>%  filter(stars.x == 0)
```
####star 1

```{r}
rm(list= ls())
df_review_restaurant <- get(load("E:/MSSP/MA678/Midproj_Yelp/Data/df_review_restaurant.Rdata"));rm(review_restaurant)

###filter reviews into different star levels
#the star column of review is `stars.x`
star1.review <- df_review_restaurant %>%  filter(stars.x == 1)

# star1.review.count1 <- star1.review %>% 
#   unnest_tokens(bigram, text, token = "ngrams", n = 1)%>%
#   transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))%>%
#   filter(!bigram %in% stop_words$word ,
#           !bigram %in% "[\\s]+",
#           !bigram %in% "")%>%
#    count(bigram, sort = TRUE)

star1.review.count <- star1.review %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")
# 
# star1.review.count3 <- star1.review %>% 
#   unnest_tokens(bigram, text, token = "ngrams", n = 3)%>%
#   transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
#    separate(bigram, c("word1", "word2","word3", sep = " ")) %>%
#    filter(!word1 %in% stop_words$word ,
#           !word1 %in% "[\\s]+",
#           !word1 %in% "") %>%
#    filter(!word2 %in% stop_words$word,
#           !word2 %in% "[\\s]+",
#           !word2 %in% "")%>%
#    filter(!word3 %in% stop_words$word,
#           !word3 %in% "[\\s]+",
#           !word3 %in% "")%>%
#    count(word1, word2,word3, sort = TRUE) %>%
#    unite(bigram, word1, word2 ,word3 ,sep = " ")

#star1.review.count <- rbind(star1.review.count1,
#                            star1.review.count2)

save(star1.review.count, file = "data/star1.review.count.Rdata")

star1_review_wordcloud <- wordcloud(star1.review.count$bigram,star1.review.count$n,max.words = 500,color = "royalblue")
star1_review_wordcloud2 <- wordcloud2(star1.review.count, shape = 'circle', color = "darkorchid")

##save wordcloud as html or pdf
#install.packages("webshot")

# save it in html
library("htmlwidgets")
saveWidget(star1_review_wordcloud2,"yelp_star1_review_wordcloud2.html",selfcontained = F)
# and in pdf
#webshot("yelp_star1_review_wordcloud2.html","star1_review_wordcloud2.pdf", delay =5, vwidth = 480, vheight=480)
```


####star 2
```{r}
##load data
rm(list= ls())
df_review_restaurant <- get(load("E:/MSSP/MA678/Midproj_Yelp/Data/df_review_restaurant.Rdata"));rm(review_restaurant)

###filter reviews into different star levels
#the star column of review is `stars.x`
star2.review <- df_review_restaurant %>%  filter(stars.x == 2)

star2.review.count1 <- star2.review[1:(nrow(star2.review)/2),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")

star2.review.count2 <- star2.review[(nrow(star2.review)/2):nrow(star2.review),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")


star2.review.count <- rbind(star2.review.count1,star2.review.count2)
rm(star2.review.count1,star2.review.count2)

star2.review.count %<>% group_by(bigram) %>% mutate(nn= sum(n)) %>% select(-n)
save(star2.review.count, file = "data/star2.review.count.Rdata")


wordcloud(star2.review.count$bigram,star2.review.count$nn,max.words = 1000,color = "forestgreen")
star2_review_wordcloud2 <- wordcloud2(star2.review.count, shape = 'circle', color = "forestgreen",size = 0.3)


saveWidget(star2_review_wordcloud2,"yelp_star2_review_wordcloud2.html",selfcontained = F)
# and in pdf
webshot("yelp_star2_review_wordcloud2.html","star2_review_wordcloud2.pdf", delay =5, vwidth = 480, vheight=480)

```

####star 3

```{r}
##load data
rm(list= ls())
df_review_restaurant <- get(load("E:/MSSP/MA678/Midproj_Yelp/Data/df_review_restaurant.Rdata"));rm(review_restaurant)

###filter reviews into different star levels
#the star column of review is `stars.x`
star3.review <- df_review_restaurant %>%  filter(stars.x == 3)

####################
star3.review.count1 <- star3.review[1:(nrow(star3.review)/2),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")

star3.review.count2 <- star3.review[(nrow(star3.review)/2):nrow(star3.review),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")


star3.review.count <- rbind(star3.review.count1,star3.review.count2)

star3.review.count %<>% group_by(bigram) %>% mutate(nn= sum(n)) %>% select(-n)
save(star3.review.count, file = "data/star3.review.count.Rdata")



wordcloud(star3.review.count$bigram,star3.review.count$nn,max.words = 1000,color = "royalblue")
star3_review_wordcloud2 <- wordcloud2(star3.review.count, shape = 'circle', color = "royalblue",size = .3)

saveWidget(star3_review_wordcloud2,"yelp_star3_review_wordcloud2.html",selfcontained = F)
# and in pdf
webshot("yelp_star3_review_wordcloud2.html","star3_review_wordcloud2.pdf", delay =5, vwidth = 480, vheight=480)


```

####star 4

```{r}
##load data
rm(list= ls())
df_review_restaurant <- get(load("E:/MSSP/MA678/Midproj_Yelp/Data/df_review_restaurant.Rdata"));rm(review_restaurant)

###filter reviews into different star levels
#the star column of review is `stars.x`
star4.review <- df_review_restaurant %>%  filter(stars.x == 4)

#############
star4.review.count1 <- star4.review[1:(nrow(star4.review)/3),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")

star4.review.count2 <- star4.review[(nrow(star4.review)/3+1):(nrow(star4.review)/3*2),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")

star4.review.count3 <- star4.review[(nrow(star4.review)/3*2+1):nrow(star4.review),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")


star4.review.count <- rbind(star4.review.count1,star4.review.count2,star4.review.count3)

star4.review.count %<>% group_by(bigram) %>% mutate(nn= sum(n)) %>% select(-n)
save(star4.review.count, file = "data/star4.review.count.Rdata")


wordcloud(star4.review.count$bigram,star4.review.count$nn,max.words = 1000,color = "coral")
star4_review_wordcloud2 <- wordcloud2(star4.review.count, shape = 'circle', color = "coral",size = .3)

saveWidget(star4_review_wordcloud2,"yelp_star4_review_wordcloud2.html",selfcontained = F)
# and in pdf
webshot("yelp_star4_review_wordcloud2.html","star4_review_wordcloud2.pdf", delay =5, vwidth = 480, vheight=480)


```


####star 5
```{r}

##load data
rm(list= ls())
df_review_restaurant <- get(load("E:/MSSP/MA678/Midproj_Yelp/Data/df_review_restaurant.Rdata"));rm(review_restaurant)

###filter reviews into different star levels
#the star column of review is `stars.x`
star5.review <- df_review_restaurant %>%  filter(stars.x == 5)

#############

star5.review.count1 <- star5.review[1:(nrow(star5.review)/3),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")

star5.review.count2 <- star5.review[(nrow(star5.review)/3):(nrow(star5.review)/3*2),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")

star5.review.count3 <- star5.review[(nrow(star5.review)/3*2):nrow(star5.review),] %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)%>%
  transmute(bigram = str_extract(bigram , "[a-z'\\s]+"))  %>%
   separate(bigram, c("word1", "word2", sep = " ")) %>%
   filter(!word1 %in% stop_words$word ,
          !word1 %in% "[\\s]+",
          !word1 %in% "") %>%
   filter(!word2 %in% stop_words$word,
          !word2 %in% "[\\s]+",
          !word2 %in% "")%>%
   count(word1, word2, sort = TRUE) %>%
   unite(bigram, word1, word2 ,sep = " ")




star5.review.count <- rbind(star5.review.count1,star5.review.count2,star5.review.count3)

star5.review.count %<>% group_by(bigram) %>% mutate(nn= sum(n)) %>% select(-n)
save(star5.review.count, file = "data/star5.review.count.Rdata")



wordcloud(star5.review.count$bigram,star5.review.count$nn,max.words = 1000,color = "tomato")
star5_review_wordcloud2 <- wordcloud2(star5.review.count, shape = 'circle', color = "tomato",size=.3)

saveWidget(star5_review_wordcloud2,"yelp_star5_review_wordcloud2.html",selfcontained = F)
# and in pdf
webshot("yelp_star5_review_wordcloud2.html","star5_review_wordcloud2.pdf", delay =5, vwidth = 480, vheight=480)


```



```{r}
```


































