---
title: "EDA"
author: "Xiang XU"
date: "December 2, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(knitr,ggplot2, tidyverse, dplyr, ggraph, stringr, wordcloud, tidytext,tidyr,lubridate, widyr,jsonlite,sentimentr, benford.analysis, magrittr)

```

```{r}
##load prepared data
rm(list = ls())
user_info <- get(load("./Dataset/business_info.Rdata"));rm("df_business_info")
```


###Restaurant category EDA

Based on the count of the retuarants' categories, we categorize them into several big types.

Now we have 17 main restuarant categories: "Italian", "French","Vietnamese",  "Chinese", "Mediterranean","Korean", "Greek", "Middle Eastern" ,"Canadian","German","Irish","Indian", "Thai" , "Mexican","Portuguese","Japanese","American". And their counts.

```{r}
#read data
restaurant_info <- get(load(( "dataset/restaurant_info.Rdata")))
restaurant_category_count <- read.csv(file = "dataset/restaurant_category_count.csv")
```

How's the rating of resturants group by categories?
```{r,fig.height=3,fig.width=4}

summary(restaurant_info$stars)

ggplot(restaurant_info,aes(x= stars ,y = ..density..))+
  geom_density(fill="coral", colour=NA, adjust =2.5)
```
```{r,fig.height=16,fig.width=16}
#sapply(x= restaurant_info$stars, INDEX = as.factor(unique(restaurant_info$categ.temp)), FUN =summary())
restaurant_summary <- 
restaurant_info %>% group_by(categ.temp)%>% 
  transmute(mean = round(mean(stars),3),sd = round(sd(stars),3),
            Q1 =quantile(stars, probs = .25),
            Q3 =quantile(stars, probs = .75))%>%
  unique()%>%
  arrange(desc(mean))
kable(restaurant_summary,caption = "stars summary by category")

# restaurant_info <- restaurant_info %>% 
#   group_by(categ.temp)%>%  mutate(mean = round(mean(stars),3)) %>% ungroup()

ggplot(restaurant_info) +
  aes(x= stars ,y = ..density.., group = categ.temp )+
  #geom_histogram(fill = "cornsilk", "color" = "grey60",size =.2) +
  aes(x=stars, fill = categ.temp,color = categ.temp)+geom_density(alpha =1, adjust =2)+
  #facet_grid( categ.temp~ ., scales="free_y", space="free_y" ) +
  # geom_vline(xintercept = mean)+
  facet_wrap(~categ.temp)+
  theme(legend.position = "none")
  
```


```{r}
ggplot(restaurant_info,aes(x= factor(categ.temp) ,y = stars, color = categ.temp )) +
  #+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=45, hjust=1, vjust=1),legend.position = "none")



ggplot(restaurant_info,aes(x= factor(categ.temp) ,y = review_count, color = categ.temp )) +
  #+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=45, hjust=1, vjust=1),legend.position = "none")
```

too many outliers inreview count

replace outliers by using "outlier rule" q +/- (1.5 * H),

```{r}
change_outliers <- function(x, na.rm = TRUE, ...) {
  qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
  H <- 1.5 * IQR(x, na.rm = na.rm)
  y <- x
  y[x < (qnt[1] - H)] <- qnt[1] - H
  y[x > (qnt[2] + H)] <- qnt[2] + H
  y
}


restaurant_info$review_count_rmout <- change_outliers(restaurant_info$review_count)
  
ggplot(restaurant_info,aes(x= factor(categ.temp) ,y = review_count_rmout, color = categ.temp )) +
  #+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=45, hjust=1, vjust=1),legend.position = "none")
```

###RestaurantsPriceRange2

```{r}
summary(restaurant_info$RestaurantsPriceRange2)

ggplot(restaurant_info,aes(x=RestaurantsPriceRange2 ))+
  geom_histogram(fill="coral", colour=NA,stat = "count")

ggplot(restaurant_info,aes(x=RestaurantsPriceRange2, fill=categ.temp, colour=categ.temp))+
  geom_histogram(stat = "count") +
  facet_wrap( ~ categ.temp) +
  theme(legend.position = "none")

```

####relation between RestaurantsPriceRange2 & stars

```{r}
ggplot(restaurant_info,aes(x=RestaurantsPriceRange2, y= stars,color="lightskynlue"))+
  geom_point(position=position_jitter(width=.3, height=0.2))+
  #facet_wrap(~categ.temp)+
  theme(legend.position = "none")

ggplot(restaurant_info,aes(x=RestaurantsPriceRange2, y= stars, color=categ.temp))+
  geom_point(position=position_jitter(width=.3, height=0.2))+
  facet_wrap(~categ.temp)+
  theme(legend.position = "none")
```

#Combine data together, explore sentiment score affect
```{r}
rm(list=ls())
restaurant_info <- get(load(( "data/restaurant_info.Rdata")))
review_sentiment_restaurant <- get( load("E:/MSSP/MA678/Midproj_Yelp/Data/review_sentiment_restaurant.Rdata"))
```
```{r}
restaurant_info$categ.temp <- as.factor(restaurant_info$categ.temp)

restaurant_info$Parking <- ifelse(str_detect(as.character(restaurant_info$BusinessParking),"True") == TRUE,TRUE, FALSE)


#cut restaurants' stars into 2 level
restaurant_info$stars_bio <- cut(restaurant_info$stars,c(0,3.1,5),labels = c("Below Average","Above Average"))

#restaurant_info$review_cat <- cut(restaurant_info$review_count, c(0,7,20,60,200,500, 1000,5000,10000),labels = c(1:8))

#look at how many NA does colmun have
na_count <-data.frame(sapply(restaurant_info, function(y) sum(length(which(is.na(y))))))


restaurant_info_nona <- na.omit(restaurant_info %>%
                                  dplyr::select(business_id , stars_bio,review_count , categ.temp , Parking, RestaurantsPriceRange2, NoiseLevel, RestaurantsTakeOut, RestaurantsDelivery ))

review_sentiment_restaurant %<>% dplyr::select(business_id, stars.x, review_sentiment)

restaurant_allinfo <- restaurant_info_nona %>% inner_join(review_sentiment_restaurant, by ="business_id")
colnames(restaurant_allinfo)

```

##multinomial

```{r, fig.width=6, fig.height=6}
#fit an ordered multinomial logit model.
fit.polr2 <- polr(ordered(stars_int) ~  review_count + categ.temp + RestaurantsPriceRange2 + NoiseLevel +Parking +RestaurantsTakeOut + RestaurantsDelivery + review_sentiment +stars.x, data = restaurant_allinfo )
display(fit.polr2)

# ##make prediction
# predx2 <- na.omit(expand.grid(review_cat =unique(restaurant_info$review_cat),
#                      categ.temp =unique(restaurant_info$categ.temp),
#                      RestaurantsPriceRange2 = unique(restaurant_info$RestaurantsPriceRange2) ,
#                      NoiseLevel = unique(restaurant_info$NoiseLevel),
#                      Parking = c(TRUE ,FALSE),
#                      RestaurantsTakeOut = c(TRUE ,FALSE),
#                      RestaurantsDelivery = c(TRUE ,FALSE)))
# 
# predy2 <- predict(fit.polr2, newdata = predx2, type = "prob")

obsmat2 <-model.matrix(~-1+as.factor(stars_int) , data= restaurant_info)
fitted2 <- fitted(fit.polr2)
resdimat2<-obsmat2[1:nrow(fitted2),]-fitted2

par(mfrow=c(3,2))
binnedplot(fitted2[,1],resdimat2[,1])
binnedplot(fitted2[,2],resdimat2[,2])
binnedplot(fitted2[,3],resdimat2[,3])
binnedplot(fitted2[,4],resdimat2[,4])
binnedplot(fitted2[,5],resdimat2[,5])
```



##logistic
```{r}
fit.logistic <- glm(stars_bio ~  review_count + categ.temp + RestaurantsPriceRange2 + NoiseLevel +Parking +RestaurantsTakeOut + RestaurantsDelivery + review_sentiment +stars.x , data = restaurant_allinfo,family = binomial(link = "logit"))
display(fit.logistic)

#look at the model fit
marginalModelPlots(fit.logistic)

binnedplot(fitted(fit.logistic),residuals(fit.logistic, type = "response"))

```

